Global Life Expectancy: Unraveling Health and Economic Determinants (2015-2020)\thanks{Code and data are available at: \url{https://github.com/wendyhuan/lifeexpectancy}.}

### 2024-12-04 paper/paper.tex
comi

@@

The goal of the Bayesian model is to incorporate prior knowledge, such
as insights from previous studies or analyses, into the selection of the
model. To predict the outcome of the life expectancy of people from
different regions, in this paper, we developed a linear regression
models using R (R Core Team 2023). The outcome variable,
\textbf{\texttt{Life\ Expectancy}}, is a continuous and represents the
average number of years a person is expected to live, assuming all
related resources remain constant throughout their lifetime. The model
aim to estimate and predict the life expectancy of people under
different gender, region and income group. The normal Gaussian
distribution is effective when used for modeling scenarios where the
residuals of the data aare assumed to be independent nd normally
distributed around the regression line. The GAM allows for capturing
potential non-linear relationships between the predictors and the
outcome.

@@

\begin{itemize}
\item
  \(yi\) is the outcome variable (Life Expectancy)for the i-th country.
\item
  \(_i\) represents the expected value of \(yi\), modeled as a linear
  combination of the predictors: Gender, Region, and Income Group.
\item
  \(Gender\) is the gender of the individual.
\item
  \(Income Group\) is the income group of the country.
\item
  \(\epsilon_i\) is the error term, assumed to be normally distributed
  with a mean of 0 and constant variance \(ϵ_i​∼N(0,\sigma^2)\)
\end{itemize}

This GAM model allows for smooth, non-linear effects of continuous
predictors (\textbf{\texttt{age}} and \textbf{\texttt{races\_count}})
while keeping the categorical predictors
(\textbf{\texttt{Income\_Group}} and \textbf{\texttt{iaaf\_category}})
in a linear framework.

Appendix~\ref{sec-model-details}.

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

@@

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

@@

RMSE

Out-of- Sample testing

@@

\subsubsection{Idealized Survey}\label{idealized-survey}

\textbf{Survey: Understanding Life Expectancy and Influencing Factor}

Thank you for participating in this survey. This survey aims to gather
insights into the factors influencing life expectancy, including health
expenditure, education, ethnicity, government spending on healthcare,
and income levels. Your responses will help us understand individual
perspectives and experiences towards national policy. Participation is
voluntary, and your answers will remain anonymous.

>>>>

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

The goal of the Bayesian model is to incorporate prior knowledge, such
as insights from previous studies or analyses, into the selection of the
model. To predict the outcome of the life expectancy of people from
different regions, in this paper, we developed a linear regression
models using R (R Core Team 2023). The outcome variable,
\textbf{\texttt{Life\ Expectancy}}, is a continuous and represents the
average number of years a person is expected to live, assuming all
related resources remain constant throughout their lifetime. The model
aim to estimate and predict the life expectancy of people under
different gender, region and income group. The normal Gaussian
distribution is effective when used for modeling scenarios where the
residuals of the data are assumed to be independent nd normally
distributed around the regression line. The GAM allows for capturing
potential non-linear relationships between the predictors and the
outcome.

@@

\begin{itemize}
\item
  \(yi\) is the outcome variable (Life Expectancy)for the i-th
  observation.
\item
  \(\mu_i\): the linear predictor for life expectancy, including the
  intercept (\(\alpha\)) and the coefficients for the predictors Region,
  Country, Income Group, and Gender.
\item
  Priors for the intercept(\(\alpha\)) and the
  coefficients(\(\beta_1, \beta_2, \beta_3\)) are normal with mean 0 and
  standard deviation 2.5
\item
  \(\sigma\): the residual standard deviation, modeled as an exponential
  distribution with rate 1.
\end{itemize}

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}. More explanation of the model could be found
Appendix~\ref{sec-model-details}.

@@

The linear regression model with Gaussian likelihood was chosen for this
analysis due to its simplicity and effectiveness in modeling continuous
outcome variables, such as life expectancy. Life expectancy is
influenced by multiple factors, including region, income group, and
gender. The linear model allows us to examine the average effect of each
predictor on the outcome, assuming that the relationships between these
predictors and life expectancy are linear.

The use of normal priors for the model coefficients \(\alpha\) and
\(\beta\) reflects a belief in prior knowledge that the true values of
these parameters are centered around zero, with some uncertainty, which
is consistent with standard Bayesian modeling practices. The prior scale
of 2.5 was chosen to reflect a reasonable level of uncertainty around
the estimates without being overly restrictive.

The Gaussian distribution was selected because life expectancy data, by
nature, is continuous and expected to follow a normal distribution. The
assumption of normal residuals is consistent with the idea that
deviations from the regression line are random and normally distributed,
allowing the model to make accurate inferences about the relationship
between predictors and the outcome.

Additionally, the exponential prior on the standard deviation \(\alpha\)
captures the residual variability in life expectancy across countries
and regions. The exponential distribution was chosen because it provides
a simple and interpretable way of modeling the variability, assuming
that the data are not heavily skewed.

This approach is appropriate given the data structure and the goal of
the analysis, which is to estimate and predict life expectancy across
different countries, regions, income groups, and genders. The model's
assumptions about the data, along with its priors, allow for robust
inference in the context of population health predictions.

@@

To assess the performance of the life expectancy prediction model, two
critical metrics were used: Root Mean Squared Error (RMSE) and
Out-of-Sample Testing. These methods help ensure that the model
generalizes well to unseen data and provides reliable predictions for
life expectancy across different regions, income groups, and genders.

RMSE measures the square root of the average squared differences between
the predicted and observed values. In the context of this model, RMSE
quantifies how closely the predicted life expectancy values align with
the actual observed values. Lower RMSE values indicate better model
performance, suggesting that the model's predictions are close to the
true values. The generalizability is checked by comparing rmse\_test and
rmse\_train. Seeing the test RMSE is slightly lower than the training
RMSE, the model generalizes well.

Out-of-Sample testing is a critical component of model evaluation. In
this approach, the data is split into a training set and a test set (or
holdout set). The training set is used to fit the model, while the test
set is used to evaluate how well the model performs on new, unseen data.
For this analysis, the model was trained using a portion of the data
(80\% of the dataset) and then evaluated on the remaining data (20\% of
the dataset) that was not used during training. This method allows us to
check whether the model overfits the training data or if it can
generalize well to unseen observations.

Together, RMSE and out-of-sample testing offer a robust framework for
model validation, ensuring that the predictions made by the life
expectancy model are both accurate and generalizable.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#model\_developed \textless{}{-}}
  \CommentTok{\#readRDS(file = "\textasciitilde{}/lifeexpectancy/models/ledata\_normal\_model.rds")}

\CommentTok{\# Split the dataset into training and testing sets (80\% train, 20\% test)}
\CommentTok{\#set.seed(123)  \# Setting seed for reproducibility}
\CommentTok{\#train\_index \textless{}{-} createDataPartition(leab$\textasciigrave{}Life Expectancy\textasciigrave{}, p = 0.8, list = FALSE)}

\CommentTok{\#train\_data \textless{}{-} leab[train\_index, ]}
\CommentTok{\#test\_data \textless{}{-} leab[{-}train\_index, ]}

\CommentTok{\# Predict life expectancy using the test data}
\CommentTok{\#predictions \textless{}{-} predict(ledata\_normal\_model, newdata = test\_data)}
\end{Highlighting}
\end{Shaded}

@@

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.2895}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1754}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0614}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.0965}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1404}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1140}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.1228}}@{}}

\caption{\label{tbl-cleaned_leab}Life expectancy over countries and
years}

\tabularnewline

\caption{Life Expectancy over countries and years (first 200
rows)}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Indicator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Period
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Gender
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Life Expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Income\_Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Region
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Indicator
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Country
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Period
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Gender
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Life Expectancy
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Income\_Group
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Region
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Life expectancy at birth (years) & Afghanistan & 2020 & Male & 59.3 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2020 & Both sexes &
60.5 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2020 & Female & 61.7 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2019 & Male & 60.0 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2019 & Both sexes &
61.2 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2019 & Female & 62.5 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2018 & Male & 59.0 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2018 & Both sexes &
60.5 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2018 & Female & 62.1 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2017 & Male & 59.8 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2017 & Both sexes &
60.9 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2017 & Female & 62.1 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2016 & Male & 59.2 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2016 & Both sexes &
60.4 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2016 & Female & 61.7 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2015 & Male & 59.3 &
lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2015 & Both sexes &
60.3 & lower\_income & Asia \\
Life expectancy at birth (years) & Afghanistan & 2015 & Female & 61.5 &
lower\_income & Asia \\
Life expectancy at birth (years) & Albania & 2020 & Male & 74.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2020 & Both sexes & 76.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2020 & Female & 79.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2019 & Male & 76.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2019 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2019 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2018 & Male & 76.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2018 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2018 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2017 & Male & 76.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2017 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2017 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2016 & Male & 76.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2016 & Both sexes & 77.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2016 & Female & 79.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2015 & Male & 76.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2015 & Both sexes & 77.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Albania & 2015 & Female & 79.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Algeria & 2020 & Male & 73.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2020 & Both sexes & 74.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2020 & Female & 75.2 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2019 & Male & 76.2 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2019 & Both sexes & 76.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2019 & Female & 77.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2018 & Male & 76.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2018 & Both sexes & 76.4 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2018 & Female & 77.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2017 & Male & 76.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2017 & Both sexes & 76.4 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2017 & Female & 77.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2016 & Male & 75.9 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2016 & Both sexes & 76.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2016 & Female & 76.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2015 & Male & 75.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2015 & Both sexes & 76.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Algeria & 2015 & Female & 76.6 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2020 & Male & 60.4 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2020 & Both sexes & 62.6 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2020 & Female & 64.9 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2019 & Male & 60.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2019 & Both sexes & 62.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2019 & Female & 64.7 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2018 & Male & 60.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2018 & Both sexes & 62.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2018 & Female & 64.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2017 & Male & 59.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2017 & Both sexes & 62.0 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2017 & Female & 64.3 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2016 & Male & 59.5 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2016 & Both sexes & 61.8 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2016 & Female & 64.2 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2015 & Male & 59.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2015 & Both sexes & 61.6 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Angola & 2015 & Female & 64.1 &
lower\_middle & Africa \\
Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Male &
75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Both
sexes & 77.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2020 & Female &
79.4 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Male &
74.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Both
sexes & 75.7 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2019 & Female &
77.1 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Male &
74.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Both
sexes & 75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2018 & Female &
77.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Male &
73.9 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Both
sexes & 75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2017 & Female &
77.0 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Male &
73.8 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Both
sexes & 75.5 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2016 & Female &
77.1 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Male &
73.8 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Both
sexes & 75.6 & high\_income & North America \\
Life expectancy at birth (years) & Antigua and Barbuda & 2015 & Female &
77.2 & high\_income & North America \\
Life expectancy at birth (years) & Argentina & 2020 & Male & 73.1 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2020 & Both sexes & 76.2
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2020 & Female & 79.4 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2019 & Male & 74.0 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2019 & Both sexes & 77.0
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2019 & Female & 79.9 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2018 & Male & 73.7 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2018 & Both sexes & 76.9
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2018 & Female & 79.9 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2017 & Male & 73.6 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2017 & Both sexes & 76.6
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2017 & Female & 79.6 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2016 & Male & 73.0 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2016 & Both sexes & 76.1
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2016 & Female & 79.2 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2015 & Male & 73.3 &
upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2015 & Both sexes & 76.5
& upper\_middle & South America \\
Life expectancy at birth (years) & Argentina & 2015 & Female & 79.6 &
upper\_middle & South America \\
Life expectancy at birth (years) & Armenia & 2020 & Male & 62.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2020 & Both sexes & 69.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2020 & Female & 76.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2019 & Male & 70.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2019 & Both sexes & 75.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2019 & Female & 79.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2018 & Male & 71.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2018 & Both sexes & 75.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2018 & Female & 79.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2017 & Male & 70.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2017 & Both sexes & 75.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2017 & Female & 79.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2016 & Male & 69.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2016 & Both sexes & 74.4 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2016 & Female & 78.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2015 & Male & 69.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2015 & Both sexes & 74.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Armenia & 2015 & Female & 78.3 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Australia & 2020 & Male & 81.5 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2020 & Both sexes & 83.4
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2020 & Female & 85.2 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2019 & Male & 80.7 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2019 & Both sexes & 82.6
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2019 & Female & 84.6 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2018 & Male & 81.2 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2018 & Both sexes & 83.0
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2018 & Female & 84.9 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2017 & Male & 80.8 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2017 & Both sexes & 82.7
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2017 & Female & 84.5 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2016 & Male & 80.7 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2016 & Both sexes & 82.6
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2016 & Female & 84.5 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2015 & Male & 80.4 &
high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2015 & Both sexes & 82.3
& high\_income & Oceania \\
Life expectancy at birth (years) & Australia & 2015 & Female & 84.2 &
high\_income & Oceania \\
Life expectancy at birth (years) & Austria & 2020 & Male & 78.8 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2020 & Both sexes & 81.1 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2020 & Female & 83.3 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2019 & Male & 79.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2019 & Both sexes & 81.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2019 & Female & 83.8 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2018 & Male & 79.2 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2018 & Both sexes & 81.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2018 & Female & 83.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2017 & Male & 79.2 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2017 & Both sexes & 81.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2017 & Female & 83.5 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2016 & Male & 79.1 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2016 & Both sexes & 81.4 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2016 & Female & 83.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2015 & Male & 78.6 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2015 & Both sexes & 81.0 &
high\_income & Europe \\
Life expectancy at birth (years) & Austria & 2015 & Female & 83.3 &
high\_income & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2020 & Male & 67.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2020 & Both sexes & 71.4
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2020 & Female & 75.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2019 & Male & 73.4 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2019 & Both sexes & 75.8
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2019 & Female & 78.1 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2018 & Male & 72.6 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2018 & Both sexes & 75.1
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2018 & Female & 77.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2017 & Male & 72.2 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2017 & Both sexes & 74.6
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2017 & Female & 76.9 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2016 & Male & 71.8 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2016 & Both sexes & 74.0
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2016 & Female & 76.0 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2015 & Male & 71.7 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2015 & Both sexes & 73.6
& upper\_middle & Europe \\
Life expectancy at birth (years) & Azerbaijan & 2015 & Female & 75.5 &
upper\_middle & Europe \\
Life expectancy at birth (years) & Bahamas & 2020 & Male & 69.2 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2020 & Both sexes & 72.6 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2020 & Female & 76.0 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2019 & Male & 68.1 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2019 & Both sexes & 70.7 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2019 & Female & 73.3 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2018 & Male & 70.2 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2018 & Both sexes & 73.4 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2018 & Female & 76.5 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2017 & Male & 70.0 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2017 & Both sexes & 73.2 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2017 & Female & 76.3 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2016 & Male & 69.7 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2016 & Both sexes & 72.9 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2016 & Female & 76.1 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2015 & Male & 69.8 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2015 & Both sexes & 72.9 &
high\_income & North America \\
Life expectancy at birth (years) & Bahamas & 2015 & Female & 76.0 &
high\_income & North America \\
Life expectancy at birth (years) & Bahrain & 2020 & Male & 73.6 &
